\begin{acknowledgements}

  My first thanks go to Subramanian Ramamoorthy. I thank him for the many years
  of guidance, advice and interesting discussions that contributed to making my
  time at Edinburgh a life-changing experience. He taught me what a great
  scientist looks like and showed me the path to become one. I hope one day I'll
  be able look at myself in the mirror and see someone as hardworking and
  academically principled as he is.

  Many thanks go to the members of the RAD group - Majd Hawasly, Svetlin Penkov,
  Stefano Albrecht, Stathis Vafeias, Benjamin Rosman, Daniel Angelov, Stavros
  Gerakaris Emmanuel Kahembwe, Pavlos Andreadis, and many others - for all the
  discussions on AI, machine learning, politics, food, life and everything else.
  I especially thank Alejandro Bordallo for being the best labmate one could
  ever wish for, and Sandy Enoch for being a fantastic friend and inspiring
  roboticist.

  I thank my classmates and friends for teaching me to truly enjoy my time and
  for making the many thousands of hours spent in Appleton Tower and Forrest
  Hill a way more fun experience than I would have imagined possible. My degree
  would not have been nearly as enjoyable without all of you.

  I thank Pushmeet Kohli, Matthew Johnson and all the folks at Microsoft
  Research Cambridge for providing me with the idea behind this project and the
  support to carry it out. I thank Tejas Kulkarni for giving me constant and
  useful feedback, and for inspiring me to tackle the hard problems in AI.

  Finally my gratitude goes to my mother, my father and my brother, whose
  unconditional support has enabled me to put all my energy in this experience.
  I would not be anywhere near where I am now without them.

\end{acknowledgements}